ext_risk_copula

### 2019-01-20 ext_risk_copula.Rmd
adding ext_risk for d=0 plot : ricker and hassell : CI need to confirm

@@

@@

@@

>>>>

```{r fig_ricker_extrisk_d0, echo=F,results="hide"}
set.seed(seed)

ricker_extrisk_d0<-readRDS("./Results/ricker/ricker_extrisk_d0.RDS")
numsims<-10000
ricker_extrisk_d0$CI0.025left<-qbinom(ricker_extrisk_d0$risk_left_d0,size=numsims,prob=0.025)/numsims
ricker_extrisk_d0$CI0.975left<-qbinom(ricker_extrisk_d0$risk_left_d0,size=numsims,prob=0.975)/numsims

ricker_extrisk_d0$CI0.025right<-qbinom(ricker_extrisk_d0$risk_right_d0,size=numsims,prob=0.025)/numsims
ricker_extrisk_d0$CI0.975right<-qbinom(ricker_extrisk_d0$risk_right_d0,size=numsims,prob=0.975)/numsims

pdf("./Results/ricker/ricker_extrisk_d0.pdf",height = 6,width=6)

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,angle=90,length=0.05,col=rgb(1,0,0,0.5),code=3)

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.05,col=rgb(0,0,1,0.5),code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

dev.off()
```

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ricker/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r fig_hassell_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
hassell_extrisk_d0<-readRDS("./Results/hassell/hassell_extrisk_d0.RDS")

hassell_extrisk_d0$CI0.025left<-qbinom(hassell_extrisk_d0$risk_left_d0,size=numsims,prob=0.025)/numsims
hassell_extrisk_d0$CI0.975left<-qbinom(hassell_extrisk_d0$risk_left_d0,size=numsims,prob=0.975)/numsims

hassell_extrisk_d0$CI0.025right<-qbinom(hassell_extrisk_d0$risk_right_d0,size=numsims,prob=0.025)/numsims
hassell_extrisk_d0$CI0.975right<-qbinom(hassell_extrisk_d0$risk_right_d0,size=numsims,prob=0.975)/numsims

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.05,col=rgb(1,0,0,0.5),code=3)

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.05,col=rgb(0,0,1,0.5),code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

dev.off()
```

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199); numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/hassell/hassell_extrisk_d0.pdf){ width=40%, height=40% }
